---
title: "PAVO_anonymous"
output: html_document
date: "2024-07-12"
---
#Load required packages 

```{r packages }
library(curl)
library(pavo)
library(dbplyr)
library(ggplot2)
```

# Limenitis (mimic): Dorsal Hindwing Blue Patch {.tabset}

## Dorsal hindwing blue spectra data for real wings for limenitis arthemis 

```{r load real wing data }
r <- curl(...)
real_lim_HW_blue <- read.csv(r, header = TRUE, sep = ",")

# convert CSV to rspec object
real_lim_HW_blue.rspec <- as.rspec(real_lim_HW_blue)


#smooth spectra plots 
real_lim_HW_blue.prspec <- procspec(
  real_lim_HW_blue.rspec,
  opt =  "smooth",
  fixneg = "zero",
  span = 0.25,
  bins = 20
)
```

```{r visualize data}
explorespec(real_lim_HW_blue.prspec)
plot(real_lim_HW_blue.prspec)
```

```{r aggregate specs}
mean.real_lim_HW_blue.prspec <- aggspec(real_lim_HW_blue.prspec, FUN = mean)
summary(mean.real_lim_HW_blue.prspec)
```

## Dorsal hindwing blue spectra data for limenitis arthemis facsimiles

```{r load facsimile data }
p <- curl(...)
fac_lim_HW_blue <- read.csv(p, header = TRUE, sep = ",")

# convert CSV to rspec object
fac_lim_HW_blue.rspec <- as.rspec(fac_lim_HW_blue)


#smooth spectra plots 
fac_lim_HW_blue.prspec <- procspec(
  fac_lim_HW_blue.rspec,
  opt =  "smooth",
  fixneg = "zero",
  span = 0.25,
  bins = 20
)
```

```{r visualize data }
explorespec(fac_lim_HW_blue.prspec)
plot(fac_lim_HW_blue.prspec)
```

```{r aggregate specs}
mean.fac_lim_HW_blue.prspec <- aggspec(fac_lim_HW_blue.prspec, FUN = mean)
summary(mean.fac_lim_HW_blue.prspec)
```

## Plot comparing real wing and facsimile data for Limenitis hindwing blue patch 

```{r plot comparison}
limenitis_HW_blue <- cbind(mean.real_lim_HW_blue.prspec, mean.fac_lim_HW_blue.prspec$dat)
limenitis_HW_blue$Wavelength <- limenitis_HW_blue$wl
limenitis_HW_blue$Real <- limenitis_HW_blue$dat
limenitis_HW_blue$Facsimile <- limenitis_HW_blue$`mean.fac_lim_HW_blue.prspec$dat`
limenitis_HW_blue <- subset(limenitis_HW_blue, select = c("Wavelength", "Real", "Facsimile"))
limenitis_HW_blue

limenitis_HW_blue.rspec <- as.rspec(limenitis_HW_blue)
limHWB_plot <- plot(limenitis_HW_blue.rspec, ylim = c(0, 50), lty = 1:2, col = c("black", "blue"), lwd = 2)
limHWB_plot
```

## Combining fac and real data into one dataset for alternative analysis 

I want to try running the data through the vismodel before aggregating & and calculating the means to see if it is able to account for intra-species variation when generating JND scores 

```{r merge lim HW blue data files}
lim_HWB <- merge(real_lim_HW_blue.prspec, fac_lim_HW_blue.prspec, by = "wl")
specs.fac <- subset(lim_HWB, subset = "fac") # subset function in pavo package allows you to subset out columns that contain the string "fac", which allows you to isolate all 10 facsimiles samples 
summary(lim_HWB, subset = c("B1", "B2", "B3", "H1"))

# extract first component of filenames containing species names
type <- do.call(rbind, strsplit(names(lim_HWB), "_"))[, 1]
lim_HWB_fac <- subset(lim_HWB, subset = type == "fac")
lim_HWB_real <- subset(lim_HWB, subset = type == "real")
```

```{r compare plot with SD}
par(mfrow = c(1, 2))

lim_HWB <- merge(real_lim_HW_blue.prspec, fac_lim_HW_blue.prspec, by = "wl")
type <- do.call(rbind, strsplit(names(lim_HWB), "_"))[, 1]

# Plot using median and standard deviation, default colours
lim_HWB_plot <- aggplot(lim_HWB, type, 
        FUN.center = median, 
        ylim = c(0, 50),
        alpha = 0.3, 
        lty = 1:2, 
        lcol = c("darkblue", "darkred"), 
        shadecol = c("darkblue", "darkred"),
        lwd = 2, 
        legend = FALSE)

legend(440, 9, legend=c("Real Wings", "Facsimile"),
       col=c("darkblue", "darkred"), lty=1:2, lwd = 2, box.lty=0)
text(600, 50, "JND = 0.69")
```

## Calculation of JNDs for Limenitis hindwing blue patch 

Colour distances are obtained by weighting the Euclidean distance of the photoreceptor quantum catches by the Weber fraction of the cones (ΔS). These measurements are in units of Just Noticeable Differences (JNDs), where distances over a certain threshold (usually 1) are considered to be discernible under the conditions considered (e.g., backgrounds, illumination). 

```{r visual model & JND scores}
vis.model <- vismodel(rspecdata = limenitis_HW_blue.rspec, visual = 'bluetit', illum = 'bluesky', trans = 'bluetit', qcatch = 'fi', bkg = 'green', vonkries = TRUE)
vis.model
JND <- coldist(vis.model,noise = 'neural', n = c(0.37, 0.7, 0.99, 1.0)) 
JND
# Warning: Quantum catch are relative, distances may not be meaningful 
```

# Battus (model): Dorsal Hindwing Blue Patch {.tabset}

## Dorsal hindwing blue spectra data for real wings for battus philenor

```{r load real wing data from Stavenga et al. 2014}
t <- curl(...)
real_bat_HW_blue <- read.csv(t, header = TRUE, sep = ",")
Percent_Reflectance <- (real_bat_HW_blue$reflectance)*100
real_bat_HW_blue$percent_reflectance <- Percent_Reflectance
real_bat_HW_blue <- subset(real_bat_HW_blue, select = c("wavelength", "percent_reflectance"))
real_bat_HW_blue

# convert CSV to rspec object
real_bat_HW_blue.rspec <- as.rspec(real_bat_HW_blue)


#smooth spectra plots 
real_bat_HW_blue.prspec <- procspec(
  real_bat_HW_blue.rspec,
  opt =  "smooth",
  fixneg = "zero",
  span = 0.25,
  bins = 20
)
```

```{r visualize data }
explorespec(real_bat_HW_blue.prspec)
plot(real_bat_HW_blue.prspec)
```

## Dorsal hindwing blue spectra data for battus philenor facsimiles

```{r load facsimile data }
g <- curl(...)
fac_bat_HW_blue <- read.csv(g, header = TRUE, sep = ",")

# convert CSV to rspec object
fac_bat_HW_blue.rspec <- as.rspec(fac_bat_HW_blue)


#smooth spectra plots 
fac_bat_HW_blue.prspec <- procspec(
  fac_bat_HW_blue.rspec,
  opt =  "smooth",
  fixneg = "zero",
  span = 0.25,
  bins = 20
)
```

```{r visualize data }
explorespec(fac_bat_HW_blue.prspec)
plot(fac_bat_HW_blue.prspec)
```

```{r aggregate specs}
mean.fac_bat_HW_blue.prspec <- aggspec(fac_bat_HW_blue.prspec, FUN = mean)
summary(mean.fac_bat_HW_blue.prspec)
```

## Plot comparing real wing and facsimile data for battus hindwing blue patch 

```{r compare plot}
battus_HW_blue <- cbind(real_bat_HW_blue.prspec, mean.fac_bat_HW_blue.prspec$dat)
battus_HW_blue$Wavelength <- battus_HW_blue$wl
battus_HW_blue$Real <- battus_HW_blue$percent_reflectance
battus_HW_blue$Facsimile <- battus_HW_blue$`mean.fac_bat_HW_blue.prspec$dat`
battus_HW_blue <- subset(battus_HW_blue, select = c("Wavelength", "Real", "Facsimile"))
battus_HW_blue

battus_HW_blue.rspec <- as.rspec(battus_HW_blue)
batHWB_plot <- plot(battus_HW_blue.rspec, ylim = c(0, 50), lty = 1:2, col = c("black", "blue"), lwd = 2)
batHWB_plot
```

## Combining fac and real data into one dataset for alternative analysis 

I want to try running the data through the vismodel before aggregating & and calculating the means to see if it is able to account for intra-species variation when generating JND scores 

```{r merge bat HW blue data files}
bat_HWB <- merge(real_bat_HW_blue.prspec, fac_bat_HW_blue.prspec, by = "wl")
colnames(bat_HWB)[2] <- "real_1" 

specs.fac <- subset(bat_HWB, subset = "fac") # subset function in pavo package allows you to subset out columns that contain the string "fac", which allows you to isolate all 10 facsimiles samples 

# extract first component of filenames containing species names
type <- do.call(rbind, strsplit(names(bat_HWB), "_"))[, 1]
bat_HWB_fac <- subset(bat_HWB, subset = type == "fac")
bat_HWB_real <- subset(bat_HWB, subset = type == "real")
```

## Calculation of JNDs for Battus hindwing blue patch 

Colour distances are obtained by weighting the Euclidean distance of the photoreceptor quantum catches by the Weber fraction of the cones (ΔS). These measurements are in units of Just Noticeable Differences (JNDs), where distances over a certain threshold (usually 1) are considered to be discernible under the conditions considered (e.g., backgrounds, illumination). 

```{r visual model and JND scores}
vis.model2 <- vismodel(rspecdata = battus_HW_blue.rspec, visual = 'bluetit', illum = 'bluesky', trans = 'bluetit', qcatch = 'fi', bkg = 'green', vonkries = TRUE)
vis.model2
JND2 <- coldist(vis.model2,noise = 'neural', n = c(0.37, 0.7, 0.99, 1.0)) 
JND2
# Warning: Quantum catch are relative, distances may not be meaningful 
```

# Figure comparing reflectance spectra for battus and limenitis 

```{r pavo figure}
par(mfrow = c(1, 2))

lim_HWB <- merge(real_lim_HW_blue.prspec, fac_lim_HW_blue.prspec, by = "wl")
type <- do.call(rbind, strsplit(names(lim_HWB), "_"))[, 1]

# Plot using median and standard deviation, default colours
lim_HWB_plot <- aggplot(lim_HWB, type, 
        FUN.center = median, 
        ylim = c(0, 50),
        alpha = 0.3, 
        lty = 1:2, 
        lcol = c("darkblue", "darkred"), 
        shadecol = c("darkblue", "darkred"),
        lwd = 3, 
        cex.axis =2,
        cex.lab = 2,
        legend = FALSE)

legend(440, 7, legend=c("Real Wings", "Facsimile"),
       col=c("darkblue", "darkred"), lty=1:2, lwd = 3, box.lty=0, cex = 2)
text(600, 50, "JND = 0.69", cex = 2)

bat_HWB <- merge(real_bat_HW_blue.prspec, fac_bat_HW_blue.prspec, by = "wl")
colnames(bat_HWB)[2] <- "real_1" 

specs.fac <- subset(bat_HWB, subset = "fac") # subset function in pavo package allows you to subset out columns that contain the string "fac", which allows you to isolate all 10 facsimiles samples 

# extract first component of filenames containing species names
type <- do.call(rbind, strsplit(names(bat_HWB), "_"))[, 1]

# Plot using median and standard deviation, default colours
bat_HWB_plot <- aggplot(bat_HWB, type, 
        FUN.center = median, 
        ylim = c(0, 50),
        alpha = 0.3, 
        lty = 1:2, 
        lcol = c("darkblue", "darkred"), 
        shadecol = c("darkblue", "darkred"),
        lwd = 3, 
        cex.axis = 2,
        cex.lab = 2,
        legend = FALSE)

legend(440, 7, legend=c("Real Wings", "Facsimile"),
       col=c("darkblue", "darkred"), lty=1:2, lwd = 3, box.lty=0, cex = 2)
text(600, 50, "JND = 1.42", cex=2)
```
# Figure code outside of markdown format for saving purposes 

par(mfrow = c(1, 2))

lim_HWB <- merge(real_lim_HW_blue.prspec, fac_lim_HW_blue.prspec, by = "wl")
type <- do.call(rbind, strsplit(names(lim_HWB), "_"))[, 1]

# Plot using median and standard deviation, default colours
lim_HWB_plot <- aggplot(lim_HWB, type, 
        FUN.center = median, 
        ylim = c(0, 50),
        alpha = 0.3, 
        lty = 1:2, 
        lcol = c("darkblue", "darkred"), 
        shadecol = c("darkblue", "darkred"),
        lwd = 3, 
        cex.axis =2,
        cex.lab = 2,
        legend = FALSE)

legend(440, 7, legend=c("Real Wings", "Facsimile"),
       col=c("darkblue", "darkred"), lty=1:2, lwd = 3, box.lty=0, cex = 2)
text(600, 50, "JND = 0.69", cex = 2)

bat_HWB <- merge(real_bat_HW_blue.prspec, fac_bat_HW_blue.prspec, by = "wl")
colnames(bat_HWB)[2] <- "real_1" 

specs.fac <- subset(bat_HWB, subset = "fac") # subset function in pavo package allows you to subset out columns that contain the string "fac", which allows you to isolate all 10 facsimiles samples 

# extract first component of filenames containing species names
type <- do.call(rbind, strsplit(names(bat_HWB), "_"))[, 1]

# Plot using median and standard deviation, default colours
bat_HWB_plot <- aggplot(bat_HWB, type, 
        FUN.center = median, 
        ylim = c(0, 50),
        alpha = 0.3, 
        lty = 1:2, 
        lcol = c("darkblue", "darkred"), 
        shadecol = c("darkblue", "darkred"),
        lwd = 3, 
        cex.axis = 2,
        cex.lab = 2,
        legend = FALSE)

legend(440, 7, legend=c("Real Wings", "Facsimile"),
       col=c("darkblue", "darkred"), lty=1:2, lwd = 3, box.lty=0, cex = 2)
text(600, 50, "JND = 1.42", cex=2)




<!-- # OLD CODE:  -->
<!-- ```{r} -->
<!-- vismodel_limHWB <- vismodel(limenitis_HW_blue.rspec,  -->
<!--                             qcatch = "fi", -->
<!--                             visual = "avg.uv", -->
<!--                             achromatic = "bt.dc", -->
<!--                             illum = "bluesky", -->
<!--                             vonkries = T, scale = 30, bkg = "green", -->
<!--                             relative = TRUE) -->
<!-- vismodel_limHWB -->
<!-- summary(vismodel_limHWB) -->
<!-- vismodel_limHWB_JND <- coldist(vismodel_limHWB) -->
<!-- vismodel_limHWB_JND -->
<!-- ``` -->
<!-- ## Limenitis (mimic): Dorsal Forewing Black Patch {.tabset} -->

<!-- ### Dorsal forewing black spectra data for real wings for limenitis arthemis  -->

<!-- ```{r} -->
<!-- b <- curl() -->
<!-- real_lim_FW_black <- read.csv(b, header = TRUE, sep = ",") -->

<!-- # convert CSV to rspec object -->
<!-- real_lim_FW_black.rspec <- as.rspec(real_lim_FW_black) -->


<!-- #smooth spectra plots  -->
<!-- real_lim_FW_black.prspec <- procspec( -->
<!--   real_lim_FW_black.rspec, -->
<!--   opt =  "smooth", -->
<!--   fixneg = "zero", -->
<!--   span = 0.25, -->
<!--   bins = 20 -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- explorespec(real_lim_FW_black.prspec) -->
<!-- plot(real_lim_FW_black.prspec) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- mean.real_lim_FW_black.prspec <- aggspec(real_lim_FW_black.prspec, FUN = mean) -->
<!-- summary(mean.real_lim_FW_black.prspec) -->
<!-- ``` -->

<!-- ### Dorsal forewing black spectra data for limenitis arthemis facsimiles -->

<!-- ```{r} -->
<!-- fac_lim_FW_black <- read.csv(s, header = TRUE, sep = ",") -->

<!-- # convert CSV to rspec object -->
<!-- fac_lim_FW_black.rspec <- as.rspec(fac_lim_FW_black) -->


<!-- #smooth spectra plots  -->
<!-- fac_lim_FW_black.prspec <- procspec( -->
<!--   fac_lim_FW_black.rspec, -->
<!--   opt =  "smooth", -->
<!--   fixneg = "zero", -->
<!--   span = 0.25, -->
<!--   bins = 20 -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- explorespec(fac_lim_FW_black.prspec) -->
<!-- plot(fac_lim_FW_black.prspec) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- mean.fac_lim_FW_black.prspec <- aggspec(fac_lim_FW_black.prspec, FUN = mean) -->
<!-- summary(mean.fac_lim_FW_black.prspec) -->
<!-- ``` -->

<!-- ### Plot comparing real wing and facsimile data for Limenitis forewing black patch  -->

<!-- ```{r} -->
<!-- limenitis_FW_black <- cbind(mean.real_lim_FW_black.prspec, mean.fac_lim_FW_black.prspec$dat) -->
<!-- limenitis_FW_black$Wavelength <- limenitis_FW_black$wl -->
<!-- limenitis_FW_black$Real <- limenitis_FW_black$dat -->
<!-- limenitis_FW_black$Facsimile <- limenitis_FW_black$`mean.fac_lim_FW_black.prspec$dat` -->
<!-- limenitis_FW_black <- subset(limenitis_FW_black, select = c("Wavelength", "Real", "Facsimile")) -->
<!-- limenitis_FW_black -->

<!-- limenitis_FW_black.rspec <- as.rspec(limenitis_FW_black) -->
<!-- limFWBk_plot <- plot(limenitis_FW_black.rspec, ylim = c(0, 50), lty = 1:2, col = c("black", "blue"), lwd = 2) -->
<!-- limFWBk_plot -->
<!-- ``` -->

<!-- ```{r} -->
<!-- lim_FWBk <- merge(real_lim_FW_black.prspec, fac_lim_FW_black.prspec, by = "wl") -->
<!-- specs.fac <- subset(lim_FWBk, subset = "fac") # subset function in pavo package allows you to subset out columns that contain the string "fac", which allows you to isolate all 10 facsimiles samples  -->
<!-- lim_FWBk_fixneg <- procspec(lim_FWBk, fixneg = "zero") -->
<!-- summary(lim_FWBk_fixneg, subset = c("B1", "B2", "B3", "H1")) -->

<!-- # extract first component of filenames containing species names -->
<!-- type <- do.call(rbind, strsplit(names(lim_FWBk_fixneg), "_"))[, 1] -->
<!-- lim_FWBk_fac <- subset(lim_FWBk_fixneg, subset = type == "fac") -->
<!-- lim_FWBk_real <- subset(lim_FWBk_fixneg, subset = type == "real") -->

<!-- # Plot using median and standard deviation, default colours -->
<!-- aggplot(lim_FWBk_fixneg, type,  -->
<!--         FUN.center = median,  -->
<!--         ylim = c(0, 70), -->
<!--         alpha = 0.3, legend = TRUE) -->
<!-- ``` -->

<!-- ### Calculation of JNDs for Limenitis forewing black patch  -->

<!-- Colour distances are obtained by weighting the Euclidean distance of the photoreceptor quantum catches by the Weber fraction of the cones (ΔS). These measurements are in units of Just Noticeable Differences (JNDs), where distances over a certain threshold (usually 1) are considered to be discernible under the conditions considered (e.g., backgrounds, illumination).  -->

<!-- ```{r} -->
<!-- vismodel_limFWBk <- vismodel(limenitis_FW_black.rspec,  -->
<!--                             qcatch = "fi", -->
<!--                             visual = "avg.uv", -->
<!--                             achromatic = "bt.dc", -->
<!--                             illum = "bluesky", -->
<!--                             vonkries = T, scale = 30, bkg = "green", -->
<!--                             relative = TRUE) -->
<!-- vismodel_limFWBk_JND <- coldist(vismodel_limFWBk) -->
<!-- vismodel_limFWBk_JND -->
<!-- ``` -->


