---
title: "Is temporal synchrony necessary for effective Batesian mimicry?"
author: "Abby Robinson"
date: "12/16/2022"
output: html_document
---

# Packages

The following packages were used for this statistical analysis 

```{r packages}
library(curl)
library(ggplot2)
library(lme4)
library(DHARMa)
library(emmeans)
library("glmmTMB")
library(patchwork)
library(performance)
library(ggmap)
library(googleway)
library("rstudioapi")
library(ggpattern)
library(tidyverse)
```

We used the "DHARMa" package to check residuals and model assumptions 
```{r DHARMa Vignette}
vignette("DHARMa", package="DHARMa") ### Useful information for checking residuals/ model assumptions 
```

## Assumptions for Generalized Linear Mixed Models (GLMMs) with Poisson Distribution

1. The variance is equal to the mean. Overdispersion can occur when your variance is much higher than your mean. DHARMa provides effective tools to quantify overdispersion, and when it is present, you would want to consider quasi-Poisson, negative binomial, or zero-inflated models (see CRAN package link above). 
2. The response variable is non-negative integer data. 
3. The responses are independent from one another. 
4. The responses occur over fixed time or space. 

#Did avian predators learn to avoid facsimiles of Battus philenor during 4-day experiments? Did avian predators learn to avoid facsimiles of the control during the 4 day experiment? 

In order to address how the time delay will affect attack rates on the mimics, we first need to show that our training experiment was effective and birds learned to avoid facsimiles of battus philenor. 

I hypothesize that birds will learn to avoid the chemically defended models faster than the control, and that we will therefore see lower attack rates on the model in the last three days of the experiment compared to the control. 

Because this initial question of the project is focused on the training phase of the experiment, each of the three time-delayed experiments (four, two, one) are essentially identical replicates of each other, and therefore this data can be pooled to increase power. 

##Prepping Data 

Load data from GitHub repo using "curl()" command 

```{r pull model data}
m <- curl("https://raw.githubusercontent.com/butterfliesrcool/Temporal_Synchrony_Predation_Experiments/main/data/predation_data/Quabbin_Model_Data.csv")
model <- read.csv(m, header = TRUE, sep = ",")
head(model)

# count data looses some information that binomial data would provide, but binomial data would likely not work here due to the low overall attack rates 
# survival analysis likely didn't work with this data because attack rates are too low for this data to be analyzed as binomial data 
```

Making sure R is "reading" the variables field.day, experiment.day, field.site, species, and treatment at factors. Attacks variable should be an integer value 

```{r check data type}
# make field.day variable factor
class(model$field.day) 
model$field.day <- as.factor(model$field.day)
class(model$field.day)

# make experiment.day variable factor
class(model$experiment.day) 
model$experiment.day <- as.factor(model$experiment.day)
class(model$experiment.day)

# make site variable factor 
class(model$field.site)
model$field.site <- as.factor(model$field.site)
class(model$field.site)

# make sure attack variable is integer 
class(model$attacks) 

# make species variable factor 
class(model$species)
model$species <- as.factor(model$species)
class(model$species)

# make treatment variable factor 
class(model$treatment)
model$treatment <- as.factor(model$treatment)
class(model$treatment)
```

## Visualize Data 

```{r checking variance assumptions}
# histogram of attacks 
hist(model$attacks)  #concerns about zero inflation based on histogram? 

# check variance and mean to assess for over /  under - dispersion 
var(model$attacks)
mean(model$attacks) # variance is greater than mean, which indicates that over-dispersion might be an issue 
```

```{r aggregate}
# summarizing attacks 
aggregate(x= model$attacks, by= list(model$experiment.day, model$species), FUN=sum)

aggregate(x= model$attacks, by= list(model$treatment), FUN=sum)
```

## Model 1 (training phase)

```{r mod1 }
mod1 <- glmmTMB(attacks ~ species*experiment.day + species*treatment + (1|field.site/field.day), data=model,ziformula=~1,family=poisson) 
summary(mod1)
check_singularity(mod1) 

# no singularity issues 
# no convergence issues 
# include experiment.day as a covariate! 
```

Check residuals with "DHARMa" package 

```{r check assumptions and residuals}
packageVersion("DHARMa")
mod1simulation <- simulateResiduals(fittedModel = mod1, plot = T)

testUniformity(mod1simulation) 
testOutliers(mod1simulation)
testDispersion(mod1simulation) 
testZeroInflation(mod1simulation) 
```

Post Hoc test allows us to compare attacks on each experimental day for each species 

```{r post hoc 1}
post.hoc1 <- emmeans(mod1, pairwise ~ experiment.day|species) 
post.hoc1

emmeans(mod1, pairwise ~ treatment|species) #no significant differences between treatments during the learning phase 
```

# When is limenitis protected from predation (four-week exp, two-week exp, one-week exp, or simultaneous exp)?

Now that we have established that the bird community at the Quabbin Reservoir did learn to avoid facsimiles of the model species Battus philenor, we can explore how the birds responded to the mimics. In each location where birds learned to avoin the model, we returned at different times (4 weeks later, 2 weeks later, one week later, or simultaneously (zero weeks)), presented the mimic and the control, and examined how birds responded to the mimic under different temporal delay treatments. 

Previous lab work and models of pavlovian learning suggest that predators should be able to retain memory of negative stimuli for long periods of time after that negative stimulus is removed. Here, we are examining how long after a negative stimulus is removed predators in natural environments retain memory of that negative model stimulus & avoid mimics. 

## Prepping Data 

Load data file from GitHub repo

```{r pull mimic data }
c <- curl("https://raw.githubusercontent.com/butterfliesrcool/Temporal_Synchrony_Predation_Experiments/main/data/predation_data/Quabbin_Mimic_Data.csv")
mimic <- read.csv(c, header = TRUE, sep = ",")
head(mimic)
```

Making sure R is "reading" the variables field.day, experiment.day, field.site, species, and treatment at factors. Attacks variable should be an integer value 

```{r check data type}
# make experimental.day variable factor 
class(mimic$experiment.day) 
mimic$experiment.day <- as.factor(mimic$experiment.day)
class(mimic$experiment.day)

# make field.day variable factor
class(mimic$field.day) 
mimic$field.day <- as.factor(mimic$field.day)
class(mimic$field.day)

# make site variable factor 
class(mimic$field.site)
mimic$field.site <- as.factor(mimic$field.site)
class(mimic$field.site)

# make sure attack variable is integer 
class(mimic$attacks) # only thing that should be an integer 

# make species variable factor 
class(mimic$species)
mimic$species <- as.factor(mimic$species)
class(mimic$species)

# make treatment variable factor 
class(mimic$treatment)
mimic$treatment <- as.factor(mimic$treatment)
class(mimic$treatment)
```

## Visualize Data 

```{r check variance assumptions}
# histogram of attacks 
hist(mimic$attacks)  #concerns about zero inflation based on histogram? 

# check variance and mean to assess for over /  under - dispersion 
var(mimic$attacks)
mean(mimic$attacks) # variance is greater than mean, which indicates that over-dispersion might be an issue 
```

## Model 2 (testing phase)

Model 2 includes field.day as a random effects variable, but this model results in singularity issues 

```{r mod2}
mod2 <- glmmTMB(attacks ~ experiment.day*species + treatment*species + (1|field.site) + (1|field.day), data=mimic,ziformula=~1,family=poisson) 
summary(mod2)
check_singularity(mod2) 

# singularity issues, likely due to the field.day random effect variable 
```

```{r mod2 assumptions check}
mod2simulation <- simulateResiduals(fittedModel = mod2, plot = T)
testUniformity(mod2simulation) 
testOutliers(mod2simulation)
testDispersion(mod2simulation) 
testZeroInflation(mod2simulation) 
```

## Model 3 (testing phase)

Model 3 does not include field.day as a random effect variable, which removes the singularity issues found in the previous model 

```{r mod3}
mod3 <- glmmTMB(attacks ~ experiment.day*species + treatment*species + (1|field.site), data=mimic,ziformula=~1,family=poisson) 
summary(mod3)
check_singularity(mod3) 

#removing the field.day random effect variable removes the singularity issues, but do we want to do that?
```

```{r mod3 assumptions check }
mod3simulation <- simulateResiduals(fittedModel = mod3, plot = T)
testUniformity(mod3simulation) 
testOutliers(mod3simulation)
testDispersion(mod3simulation) 
testZeroInflation(mod3simulation) 
```

```{r post hocs for mod2 and mod3}
post.hoc2 <- emmeans(mod2, pairwise ~ species|treatment) 
#there is a significant difference in the attack rates on junonia and limenitis only in the zero week treatment (simultaneous presentation)
post.hoc2

post.hoc3 <- emmeans(mod3, pairwise ~ species|treatment)
post.hoc3 
#post hoc results are the same for mod2 and mod3
#given this, we include mod2 in the final analysis because there are biological reasons for including field.day as a random effect 


post.hoc4 <- emmeans(mod3, pairwise ~ species|treatment) 
post.hoc5 <- emmeans(mod2, pairwise ~ experiment.day|species)
# there are no significant differences in attacks on the mimic (limenitis) across the 4-day experiment. There is a significant difference between days 1 and 3 for the control (junonia), likely due to weather 
```

# Figures

## learning phase figure 

### Visualizing attack data 

```{r data length }
length(model$attacks)
```

```{r aggregate}
# Summary of attacks on facsimiles during learning  phase 
aggregate(x= model$attacks, by= list(model$experiment.day, model$species), FUN=sum)
```

### Confidence Intervals 

```{r subset B.philenor}
# subset model data (battus philenor)
b <- subset(model, species == "battus", drop = FALSE)

b_attacked <- aggregate(x=b$attacks, by = list(b$species, b$experiment.day), FUN=sum)
b_attacked
```

```{r subset J.coenia}
# subset control data (junonia coenia)
j <- subset(model, species == "junonia", drop = FALSE)
j_attacked <- aggregate(x=j$attacks, by = list(j$species, j$experiment.day), FUN=sum)
j_attacked
```

```{r Calculate SD}
# subset each day within each species to calculate a confidence interval for the count total of facsimiles attacked  each experimental day 

  # battus philenor (model)
b1 <- subset(b, experiment.day == "1", drop = FALSE)
b2 <- subset(b, experiment.day == "2", drop = FALSE)
b3 <- subset(b, experiment.day == "3", drop = FALSE)
b4 <- subset(b, experiment.day == "4", drop = FALSE)

  # junonia coenia (control)
j1 <- subset(j, experiment.day == "1", drop = FALSE)
j2 <- subset(j, experiment.day == "2", drop = FALSE)
j3 <- subset(j, experiment.day == "3", drop = FALSE)
j4 <- subset(j, experiment.day == "4", drop = FALSE)

# calculate standard deviation of attacked proportion 

  # battus philenor (model)
b1.sd <- sd(b1$attacks)
b2.sd <- sd(b2$attacks)
b3.sd <- sd(b3$attacks)
b4.sd <- sd(b4$attacks)

  # junonia coenia (control)
j1.sd <- sd(j1$attacks)
j2.sd <- sd(j2$attacks)
j3.sd <- sd(j3$attacks)
j4.sd <- sd(j4$attacks)
```


```{r new data frame with SD}
# create a new data frame with the experimental day info, attack proportion, and confidence interval for each species 

  # battus philenor (model)
battus_plot_data <- data.frame(
  Day      = b_attacked$Group.2,
  Attacked = b_attacked$x,
  SD       = c(b1.sd, b2.sd, b3.sd, b4.sd)
)
battus_plot_data

  # junonia coenia (control)
junonia_plot_data <- data.frame(
  Day      = j_attacked$Group.2,
  Attacked = j_attacked$x,
  SD       = c(j1.sd, j2.sd, j3.sd, j4.sd)
)
junonia_plot_data
```

### Battus philenor Figure 

```{r B.pilenor figure}
p_value <- tibble(
  x = c("1", "1", "3", "3"),
  y = c(24, 25, 25, 23)
)

p_value2 <- tibble(
  x = c("2", "2", "4", "4"),
  y = c(22, 23, 23, 22)
)

b.plot <- ggplot(battus_plot_data) + 

  geom_bar( aes(Day, Attacked), stat="identity", fill="grey70", width=1) + 
  ylim(0,25) +  xlab("Day") +  ylab("Facsimiles Attacked") + 
  geom_text(aes(x=Day, y=Attacked, label = Attacked), vjust = -1) +
  ggtitle(expression(bolditalic("Battus philenor"))) + 
  geom_errorbar( aes(x=Day, ymin=Attacked-SD, ymax=Attacked+SD), width=0.2, size=0.7) + 
  theme_classic() + 
  theme( aspect.ratio = 4/3, 
         plot.title = element_text(hjust = 0.5, size=17), 
         axis.title = element_text(size = 15), 
         axis.text = element_text(size = 15)) + 
  geom_line(data = p_value, 
            aes(x = x, y = y, group = 1)) +
  geom_line(data = p_value2, 
            aes(x = x, y = y, group = 1)) 
b.plot 
```

### Junonia coenia Figure 

```{r J.coenia figure}
j.plot <- ggplot(junonia_plot_data) +
     geom_bar( aes(Day, Attacked), stat="identity", fill="gray35", width=1) + 
     ylim(0,25) +  xlab("Day") +  ylab("Facsimiles Attacked") +
     geom_text(aes(x=Day, y=Attacked, label = Attacked), vjust = -1) +
     ggtitle(expression(bolditalic("Junonia coenia "))) +
     geom_errorbar( aes(x=Day, ymin=Attacked-SD, ymax=Attacked+SD), width=0.2, size=0.5) + 
     theme_classic() + theme( aspect.ratio = 4/3, 
                              plot.title = element_text(hjust = 0.5, size=17), 
                              axis.title = element_text(size = 15), axis.text = element_text(size = 15)) 
j.plot 
```

### Final Figure (Part 1)

```{r final figure}
figure = b.plot + j.plot 

# Remove title from second subplot
figure[[2]] = figure[[2]] + theme(axis.text.y = element_blank(),
                                        axis.ticks.y = element_blank(),
                                        axis.title.y = element_blank() )
figure
```

```{r save figure }
figure = b.plot + j.plot 

figure

ggsave(figure, file = "/Users/abbyrobinson/Desktop/Temporal Dynamics Project/learning_figure.pdf", width=8, height=8, units=c("in"), useDingbats=FALSE)

```


## Quabbin Reservior Transect Map 

```{r load GIS data for map}
d <- curl("https://raw.githubusercontent.com/butterfliesrcool/Temporal_Synchrony_Predation_Experiments/main/data/Quabbin_GIS_Data.csv")
map <- read.csv(d, header = TRUE, sep = ",")
head(map)
```

```{r data filtering }
map <- subset(map, select = c(experiment, site, latitude, longitude) )
head(map)
```

```{r load google API}
register_google(key = "")
```

```{r Quabbin map figure }
quab.map <- ggmap(get_googlemap(center = c(lon = -72.30, lat = 42.398),
                    zoom = 12, scale = 2,
                    maptype ='roadmap',
                    color = 'color', 
                    style=c(feature="all",element="labels",visibility="off"))) + 
            geom_point(aes(x = longitude, y = latitude, shape = experiment, color = experiment), data = map, size = 4)  + 
            theme(legend.position="right", 
                    axis.title = element_text(size = 20, face="bold"), 
                    axis.text = element_text(size = 20),
                    legend.title = element_text(face ="bold")) + 
             xlab("Longitude") + ylab("Latitude") +  labs(color = "Experiment Type", shape = "Experiment Type" ) +
             scale_color_manual(breaks = c("one", "two", "four", "sim"), 
                                values = c("darkorchid4", "darkorchid4", "darkorchid4", "red3"), 
                                labels = c("Transect 1", "Transect 2", "Transect 3", "Transect 4")) + 
             scale_shape_manual(breaks = c("one", "two", "four", "sim"), 
                                values = c(17, 16, 15, 18), 
                                labels = c("Transect 1", "Transect 2", "Transect 3", "Transect 4"))
quab.map
ggsave(quab.map, file = "/Users/abbyrobinson/Desktop/Temporal Dynamics Project/quab.map.pdf", width=15, height=10, units=c("in"), useDingbats=FALSE)

```

```{r T0 map }
map_sim <- subset(map, experiment == "sim") 
map_sim

quab_map_sim <- ggmap(get_googlemap(center = c(lon = -72.30, lat = 42.398),
                    zoom = 12, scale = 2,
                    maptype ='roadmap',
                    color = 'color', 
                    style=c(feature="all",element="labels",visibility="off"))) + 
            geom_point(aes(x = longitude, y = latitude, color = experiment), data = map_sim, size = 4)  + 
            theme(legend.position="right", 
                    axis.title = element_text(size = 20, face="bold"), 
                    axis.text = element_text(size = 20),
                    legend.title = element_text(face ="bold")) + 
             xlab("Longitude") + ylab("Latitude") + 
             scale_color_manual( values = c("darkorange2"))
quab_map_sim
```

```{r T1 map }
map_one <- subset(map, experiment == "one") 
map_one

quab_map_one <- ggmap(get_googlemap(center = c(lon = -72.30, lat = 42.398),
                    zoom = 12, scale = 2,
                    maptype ='roadmap',
                    color = 'color', 
                    style=c(feature="all",element="labels",visibility="off"))) + 
            geom_point(aes(x = longitude, y = latitude, color = experiment), data = map_one, size = 4)  + 
            theme(legend.position="right", 
                    axis.title = element_text(size = 20, face="bold"), 
                    axis.text = element_text(size = 20),
                    legend.title = element_text(face ="bold")) + 
             xlab("Longitude") + ylab("Latitude") + 
             scale_color_manual( values = c("royalblue"))
quab_map_one
```

```{r T2 map }
map_two <- subset(map, experiment == "two") 
map_two

quab_map_two <- ggmap(get_googlemap(center = c(lon = -72.30, lat = 42.398),
                    zoom = 12, scale = 2,
                    maptype ='roadmap',
                    color = 'color', 
                    style=c(feature="all",element="labels",visibility="off"))) + 
            geom_point(aes(x = longitude, y = latitude, color = experiment), data = map_two, size = 4)  + 
            theme(legend.position="right", 
                    axis.title = element_text(size = 20, face="bold"), 
                    axis.text = element_text(size = 20),
                    legend.title = element_text(face ="bold")) + 
             xlab("Longitude") + ylab("Latitude") + 
             scale_color_manual( values = c("plum4"))
quab_map_two
```

```{r T4 map }
map_four <- subset(map, experiment == "four") 
map_four

quab_map_four <- ggmap(get_googlemap(center = c(lon = -72.30, lat = 42.398),
                    zoom = 12, scale = 2,
                    maptype ='roadmap',
                    color = 'color', 
                    style=c(feature="all",element="labels",visibility="off"))) + 
            geom_point(aes(x = longitude, y = latitude, color = experiment), data = map_four, size = 4)  + 
            theme(legend.position="right", 
                    axis.title = element_text(size = 20, face="bold"), 
                    axis.text = element_text(size = 20),
                    legend.title = element_text(face ="bold")) + 
             xlab("Longitude") + ylab("Latitude") + 
             scale_color_manual( values = c("red4"))
quab_map_four
```

## Testing phase figure 

### Prepping Figure Data 

```{r aggregate by treatment}
# isolate each treatment type to visualize patterns of attack 
four_weeks   <- subset(mimic, treatment == "four", drop = FALSE) 
two_weeks    <- subset(mimic, treatment == "two", drop = FALSE) 
one_week     <- subset(mimic, treatment == "one", drop = FALSE) 
simultaneous <- subset(mimic, treatment == "zero", drop = FALSE)

four_attacks  <- aggregate(x=four_weeks$attacks, by = list(four_weeks$species), FUN=sum)
two_attacks   <- aggregate(x=two_weeks$attacks, by = list(two_weeks$species), FUN=sum)
one_attacks   <- aggregate(x=one_week$attacks, by = list(one_week$species), FUN=sum)
zero_attacks  <- aggregate(x=simultaneous$attacks, by = list(simultaneous$species), FUN=sum)
```

### Confidence Intervals 

```{r calculate SD}
# subset each species within each treatment to calculate a confidence interval for the proportion of facsimiles of each species attacked 

  # four week experiment 
lim4 <- subset(four_weeks, species == "limenitis", drop = FALSE)
jun4 <- subset(four_weeks, species == "junonia", drop = FALSE)

  # two week experiment 
lim2 <- subset(two_weeks, species == "limenitis", drop = FALSE)
jun2 <- subset(two_weeks, species == "junonia", drop = FALSE)

  # one week experiment 
lim1 <- subset(one_week, species == "limenitis", drop = FALSE)
jun1 <- subset(one_week, species == "junonia", drop = FALSE)

  # simultaneous experiment 
lim0 <- subset(simultaneous, species == "limenitis", drop = FALSE)
jun0 <- subset(simultaneous, species == "junonia", drop = FALSE)


# calculate standard deviation of attacked proportion 

  # four week experiment 
lim4.sd <- sd(lim4$attacks)
jun4.sd <- sd(jun4$attacks)

  # two week experiment 
lim2.sd <- sd(lim2$attacks)
jun2.sd <- sd(jun2$attacks)

  # one week experiment 
lim1.sd <- sd(lim1$attacks)
jun1.sd <- sd(jun1$attacks)

  # simultaneous experiment 
lim0.sd <- sd(lim0$attacks)
jun0.sd <- sd(jun0$attacks)
```

```{r new data frame with SD}
# create a new data frame with the species info, attack proportion, and confidence interval for each treatment 

  # four week experiment 
four_plot_data <- data.frame(
  Species  = four_attacks$Group.1,
  Attacks  = four_attacks$x,
  SD       = c(jun4.sd, lim4.sd)
)
four_plot_data

  # two week experiment 
two_plot_data <- data.frame(
  Species  = two_attacks$Group.1,
  Attacks  = two_attacks$x,
  SD       = c(jun2.sd, lim2.sd)
)
two_plot_data

  # one week experiment 
one_plot_data <- data.frame(
  Species = one_attacks$Group.1,
  Attacks = one_attacks$x,
  SD      = c(jun1.sd, lim1.sd)
)
one_plot_data

  # simultaneous experiment 
zero_plot_data <- data.frame(
  Species = zero_attacks$Group.1,
  Attacks = zero_attacks$x,
  SD      = c(jun0.sd, lim0.sd)
)
zero_plot_data
```

### Four Week Experiment Figure 

```{r testing phase figure }
four_plot <- ggplot(four_plot_data) +
             geom_bar_pattern(aes(Species, Attacks, pattern = Species),
                   stat = "identity", 
                   fill= c("gray35", "gray70"), 
                   width = 0.8, 
                   pattern_fill = "white",
                   pattern_angle = 90,
                   pattern_density = 0.1,
                   pattern_spacing = 0.05) + 
             ylim(0,20)  + xlab(expression(bold("Four-Week Treatment"))) +  ylab("Facsimiles Attacked") + 
             geom_text(aes(x=Species, y=Attacks, label = Attacks), vjust = -1) +
             scale_x_discrete(limits =  c("limenitis", "junonia"), 
                              labels = c("limenitis" = expression(italic("L. arthemis ")),"junonia" = expression(italic("J. coenia ")))) + 
             scale_pattern_manual(values=c('none', 'none')) + 
             geom_errorbar( aes(x=Species, ymin=Attacks-SD, ymax=Attacks+SD), width=0.2, size=0.5) + 
             theme_classic() +
             theme( aspect.ratio = 4/3, 
                    axis.title = element_text(size = 12), 
                    axis.text = element_text(size = 10), 
                    legend.position = "none") 


two_plot <- ggplot(two_plot_data) +
             geom_bar_pattern(aes(Species, Attacks, pattern = Species),
                   stat = "identity", 
                   fill= c("gray35", "gray70"), 
                   width = 0.8, 
                   pattern_fill = "white",
                   pattern_angle = 90,
                   pattern_density = 0.7,
                   pattern_spacing = 0.05) + 
             ylim(0,20)  + xlab(expression(bold("Two-Week Treatment"))) + ylab("Facsimiles Attacked") + 
             geom_text(aes(x=Species, y=Attacks, label = Attacks), vjust = -1) +
             scale_x_discrete(limits =  c("limenitis", "junonia"), 
                              labels = c("limenitis" = expression(italic("L. arthemis ")),"junonia" = expression(italic("J. coenia ")))) + 
             scale_pattern_manual(values=c('none', 'none')) + 
             geom_errorbar( aes(x=Species, ymin=Attacks-SD, ymax=Attacks+SD), width=0.2, size=0.5) + 
             geom_text(aes(x=Species, y=Attacks, label = Attacks), vjust = -1) +
             theme_classic() +
             theme( aspect.ratio = 4/3, 
                    axis.title = element_text(size = 12), 
                    axis.text = element_text(size = 10), 
                    legend.position = "none") 

one_plot <- ggplot(one_plot_data) +
             geom_bar_pattern(aes(Species, Attacks, pattern = Species),
                   stat = "identity", 
                   fill= c("gray35", "gray70"), 
                   width = 0.8, 
                   pattern_fill = "white",
                   pattern_angle = 45,
                   pattern_density = 0.9,
                   pattern_spacing = 0.05) + 
             ylim(0,20)  + xlab(expression(bold("One-Week Treatment"))) + ylab("Facsimiles Attacked") + 
             geom_text(aes(x=Species, y=Attacks, label = Attacks), vjust = -1) +
             scale_x_discrete(limits =  c("limenitis", "junonia"), 
                              labels = c("limenitis" = expression(italic("L. arthemis ")),"junonia" = expression(italic("J. coenia ")))) + 
             scale_pattern_manual(values=c('none', 'none')) + 
             geom_errorbar( aes(x=Species, ymin=Attacks-SD, ymax=Attacks+SD), width=0.2, size=0.5) + 
             theme_classic() +
             theme( aspect.ratio = 4/3, 
                    axis.title = element_text(size = 12), 
                    axis.text = element_text(size = 10), 
                    legend.position = "none") 

one_plot  

p_value <- tibble(
  x = c("limenitis", "limenitis", "junonia", "junonia"),
  y = c(18, 19, 19, 18)
)

zero_plot <- ggplot(zero_plot_data) +
             geom_bar_pattern(aes(Species, Attacks, pattern = Species),
                   stat = "identity", 
                   fill= c("gray35", "gray70"), 
                   width = 0.8, 
                   pattern_fill = "white",
                   pattern_angle = 45,
                   pattern_density = 0.1,
                   pattern_spacing = 0.05) + 
             geom_line(data = p_value, aes(x = x, y = y, group = 1)) +
             ylim(0,20)  + xlab(expression(bold("Simultaneous Treatment"))) +  ylab("Facsimiles Attacked (%)") + 
             geom_text(aes(x=Species, y=Attacks, label = Attacks), vjust = -1) +
             scale_x_discrete(limits =  c("limenitis", "junonia"), 
                              labels = c("limenitis" = expression(italic("L. arthemis ")),"junonia" = expression(italic("J. coenia ")))) + 
             scale_pattern_manual(values=c('none', 'none')) + 
             geom_errorbar( aes(x=Species, ymin=Attacks-SD, ymax=Attacks+SD), width=0.2, size=0.5) + 
             theme_classic() +
             theme( aspect.ratio = 4/3, 
                    axis.title = element_text(size = 12), 
                    axis.text = element_text(size = 10), 
                    legend.position = "none") 


fig = zero_plot + one_plot + two_plot + four_plot 

fig[[1]] = fig[[1]] + theme(axis.title.x = element_blank(), 
                            axis.text.x = element_blank())

fig[[2]] = fig[[2]] + theme(axis.title.y = element_blank(), 
                            axis.title.x = element_blank(), 
                            axis.text.x = element_blank())

fig[[3]] = fig[[3]] + theme(axis.title.y = element_blank(),
                            axis.title.x = element_blank(), 
                            axis.text.x = element_blank())

fig[[4]] = fig[[4]] + theme(axis.title.y = element_blank(), 
                            axis.title.x = element_blank(), 
                            axis.text.x = element_blank())

attack.fig <- fig + plot_layout(nrow=1)
attack.fig

ggsave(attack.fig, file = "/Users/abbyrobinson/Desktop/Temporal Dynamics Project/attack_fig.pdf", width=8, height=8, units=c("in"), useDingbats=FALSE)

```

```{r alternative figure }
four_plot <- ggplot(four_plot_data) +
             geom_bar_pattern(aes(Species, Attacks, pattern = Species),
                   stat = "identity", 
                   fill= c("gray35", "white"), 
                   width = 0.8, 
                   pattern_fill = "white",
                   pattern_angle = 90,
                   pattern_density = 0.1,
                   pattern_spacing = 0.05) + 
             ylim(0,20)  + xlab(expression(bold("Four-Week Treatment"))) +  ylab("Facsimiles Attacked") + 
             scale_x_discrete(limits =  c("limenitis", "junonia"), 
                              labels = c("limenitis" = expression(italic("L. arthemis ")),"junonia" = expression(italic("J. coenia ")))) + 
             scale_pattern_manual(values=c('none', 'crosshatch')) + 
             geom_errorbar( aes(x=Species, ymin=Attacks-SD, ymax=Attacks+SD), width=0.2, size=0.5) + 
             theme_classic() +
             theme( aspect.ratio = 4/3, 
                    axis.title = element_text(size = 15), 
                    axis.text = element_text(size = 15), 
                    legend.position = "none") 


two_plot <- ggplot(two_plot_data) +
             geom_bar_pattern(aes(Species, Attacks, pattern = Species),
                   stat = "identity", 
                   fill= c("gray35", "white"), 
                   width = 0.8, 
                   pattern_fill = "white",
                   pattern_angle = 90,
                   pattern_density = 0.7,
                   pattern_spacing = 0.05) + 
             ylim(0,20)  + xlab(expression(bold("Two-Week Treatment"))) + ylab("Facsimiles Attacked") + 
             scale_x_discrete(limits =  c("limenitis", "junonia"), 
                              labels = c("limenitis" = expression(italic("L. arthemis ")),"junonia" = expression(italic("J. coenia ")))) + 
             scale_pattern_manual(values=c('none', 'circle')) + 
             geom_errorbar( aes(x=Species, ymin=Attacks-SD, ymax=Attacks+SD), width=0.2, size=0.5) + 
             theme_classic() +
             theme( aspect.ratio = 4/3, 
                    axis.title = element_text(size = 15), 
                    axis.text = element_text(size = 15), 
                    legend.position = "none") 

one_plot <- ggplot(one_plot_data) +
             geom_bar_pattern(aes(Species, Attacks, pattern = Species),
                   stat = "identity", 
                   fill= c("gray35", "white"), 
                   width = 0.8, 
                   pattern_fill = "white",
                   pattern_angle = 45,
                   pattern_density = 0.9,
                   pattern_spacing = 0.05) + 
             ylim(0,20)  + xlab(expression(bold("One-Week Treatment"))) + ylab("Facsimiles Attacked") + 
             scale_x_discrete(limits =  c("limenitis", "junonia"), 
                              labels = c("limenitis" = expression(italic("L. arthemis ")),"junonia" = expression(italic("J. coenia ")))) + 
             scale_pattern_manual(values=c('none', 'wave')) + 
             geom_errorbar( aes(x=Species, ymin=Attacks-SD, ymax=Attacks+SD), width=0.2, size=0.5) + 
             theme_classic() +
             theme( aspect.ratio = 4/3, 
                    axis.title = element_text(size = 15), 
                    axis.text = element_text(size = 15), 
                    legend.position = "none") 

one_plot  

p_value <- tibble(
  x = c("limenitis", "limenitis", "junonia", "junonia"),
  y = c(18, 19, 19, 18)
)

zero_plot <- ggplot(zero_plot_data) +
             geom_bar_pattern(aes(Species, Attacks, pattern = Species),
                   stat = "identity", 
                   fill= c("gray35", "white"), 
                   width = 0.8, 
                   pattern_fill = "white",
                   pattern_angle = 45,
                   pattern_density = 0.1,
                   pattern_spacing = 0.05) + 
             geom_line(data = p_value, aes(x = x, y = y, group = 1)) +
             ylim(0,20)  + xlab(expression(bold("Simultaneous Treatment"))) +  ylab("Facsimiles Attacked (%)") + 
             scale_x_discrete(limits =  c("limenitis", "junonia"), 
                              labels = c("limenitis" = expression(italic("L. arthemis ")),"junonia" = expression(italic("J. coenia ")))) + 
             scale_pattern_manual(values=c('none', 'crosshatch')) + 
             geom_errorbar( aes(x=Species, ymin=Attacks-SD, ymax=Attacks+SD), width=0.2, size=0.5) + 
             theme_classic() +
             theme( aspect.ratio = 4/3, 
                    axis.title = element_text(size = 15), 
                    axis.text = element_text(size = 15), 
                    legend.position = "none") 


fig = four_plot + two_plot + one_plot + zero_plot

fig[[1]] = fig[[1]] + theme(axis.title.x = element_blank(), 
                            axis.text.x = element_blank())

fig[[2]] = fig[[2]] + theme(axis.title.y = element_blank(), 
                            axis.title.x = element_blank(), 
                            axis.text.x = element_blank())

fig[[3]] = fig[[3]] + theme(axis.title.x = element_blank(), 
                            axis.text.x = element_blank())

fig[[4]] = fig[[4]] + theme(axis.title.y = element_blank(), 
                            axis.title.x = element_blank(), 
                            axis.text.x = element_blank())

attack.fig <- fig + plot_layout(nrow=2)
attack.fig
```
